### 2013-09-30 Publications/2013-ISBI14/02-introduction.tex
ISBI2014

First approaches to
retrospective correction \cite{jezzard_correction_1995},
relied on an extra \gls*{mri} acquisition (so-called
\emph{field mapping}), that probes the inhomogeneity of the field.
A second theory-based breed of methodologies acquire a 
map of the \gls*{psf} of the \gls*{epi} readouts to correct 
for the artifact \cite{robson_measurement_1997}. 
Next generation of methodologies \cite{cordes_geometric_2000,
chiou_simple_2000}, make use of the acquisition of 
extra \gls*{epi} volumes 
with specific differences that enable correction, for instance
the opposed direction of the phase encoding gradients 
Finally, the last family of methodologies acquire an 
extra T2-weighted image, and use its anatomical correctness 
as reference to find the deformation map through nonlinear 
registration \cite{kybic_unwarping_2000,studholme_accurate_2000}.
Registration-based methods usually map
the T2 image to the so-called baseline (B0) volume 
of \gls*{dmri}. The choice of T2 is due to the strong
similarity of intensity distribution with the B0 of \gls*{dmri}
datasets. More recent works report extensions or combined
approaches of existing techniques
\cite{andersson_how_2003,zaitsev_point_2004,%
holland_efficient_2010,andersson_comprehensive_2012}.

>>>>

\Gls*{fmb} methods supposed the first approach to retrospective
correction \cite{jezzard_correction_1995}. They rely on one
extra acquisition (\emph{field mapping}), that probes the 
inhomogeneity of the field.
A second theory-based breed of methodologies acquire a 
map of the \acrlong*{psf} of the \gls*{epi} readouts to correct 
for the artifact \cite{robson_measurement_1997}. 
Next generation of methodologies \cite{cordes_geometric_2000,
chiou_simple_2000}, make use of the acquisition of 
extra \gls*{epi} volumes 
with specific differences that enable correction, for instance
the opposed direction of the phase encoding gradients. We will
refer to these methods as \gls*{reb}.
Finally, the last family of methodologies acquire an 
extra T2-weighted image, and use its anatomical correctness 
as reference to find the deformation map through nonlinear 
registration \cite{kybic_unwarping_2000,studholme_accurate_2000}.
\gls*{t2b} methods usually map
the T2 image to the \emph{baseline} volume or ``B0''
of \gls*{dmri}. The choice of T2 is due to the strong
similarity of intensity distribution with respect the B0.
More recent works report extensions or combined
approaches of existing techniques
\cite{andersson_how_2003,zaitsev_point_2004,%
holland_efficient_2010,andersson_comprehensive_2012}.
